\thetitle

### 2020-11-21 writing/results.tex
complete results description

Figure~\ref{fig:effort-table} shows the distribution of programmer effort
for the sampled interesting debugging --- in contrast to the usefulness
comparisons these results do not generalize to the full population.

>>>>

Figure~\ref{fig:effort-table} shows the distribution of programmer effort
for our sample of interesting debugging scenarios . Unlike the usefulness
comparisons above, these results do not generalize to the full population.
Still, as we discuss in section~\ref{subsec:effort}, they provide an
alternative view of the workings of the rational programmer.

There are
three immediate take-aways from the figure. First, the effort for successfully
debugging interesting scenarios (in green) for the random mode of the
rational program  follows  a normal distribution as expected.\footnote{The
random mode distribution is indistinguishable for all three semantics and thus the figure~\ref{fig:effort-table} 
only shows one plot.} In contrast, in the other modes, successful effort coalesces at
the left side of the plot, meaning that in most cases the programmer needs
to type a single component to debug a scenario. Even in the minority of
cases where a blame or exception mode has to work harder, the number of
modules that that need to be typed is small relative to the random mode.

A second point of interest is that the exceptions of
the erasure semantics either help the rational programmer immediately or 
the rational programmer fails to debug a scenario altogether (in red). This shouldn't
come as a surprise; no matter how many type annotations the programmer
adds to an erasure program, if the type checker doesn't reject the
program, running the program produces always the same outcome. Thus an
exception from the erasure's runtime has to point to the buggy component with
the first try. Otherwise the rational programmer types an irrelevant
component, runs the program again and the exception points again to the
already typed component.

A third interesting piece of information from
the figure is that every mode has failed debugging scenarios. This should
not come as a surprise to the astute
reader After all, as we
discuss above, some modes are more successful than others in certain
scenarios. Indeed any mode can fail if running a scenario results in an
exception and the exception carries no useful information about which
component the programmer should type next, e.g., because the stack trace 
does not contain frames from the component of the program.
This explains the majority of
failures to debug failed scenarios but not all. The next section takes a
closer look at these unexpected situations as part of the lessons we
extract from our experimental results.
